A Study on Common Bug Fix Patterns in Rust

### 2022-10-29 main.tex
two warnings gone, small fix

Rust is popular: as of 2022, it has ranked first, for the sixth consecutive year, in Stack Overflow's annual Developer Survey as the most-loved programming language. The number of Rust developers is growing as the need for faster and safer software increases.

>>>>

Rust is popular: as of 2022, it has ranked first, for the seventh consecutive year, in Stack Overflow's annual Developer Survey as the most-loved programming language. The number of Rust developers is growing as the need for faster and safer software increases.
